### 2018-07-12 doc/plos/text/manuscript.tex
add plot accuracy_vs_sensors
also tweak the size of all the other plots
add plot accuracy_vs_ablation
add plot accuracy_vs_abscission
covairance wording and references
I tried to make the description of the covariance estimation method
clearer, and I added references to published methods.

Estimating covariance in this situation is challenging, and while the
statistical literature suggests several approaches TODO(cite a few of them),
consensus appears to be lacking.

We begin by computing the empirical pair-wise covariance of all sensors.
However, the resulting matrix does not necessarily describe multi-dimensional
covariance (i.e. it may not be positive definite). To correct this, we shrink
this matrix toward the diagonal matrix of sensor variance. The magnitude of the
shrinkage weight is chosen to maximize the multivariate normal log-likelihood
of the available data. We subsequently use the shrunken matrix as $R$ in sensor
fusion.

@@

@@

% Don't include figures in the final version. This is just for preview.
\newgeometry{top=1.0in,left=1.0in,footskip=30pt}
\begin{figure}[p]
  \includegraphics[width=\textwidth]{../data/figures/sensor_heatmap_top.png}
  Figure 1 (top).
\end{figure}
\begin{figure}[p]
  \includegraphics[width=\textwidth]{../data/figures/sensor_heatmap_bottom.png}
  Figure 1 (bottom).
\end{figure}
\begin{figure}[p]
  \includegraphics[width=\textwidth]{../data/figures/all_nowcasts.png}
  Figure 2.
\end{figure}

>>>>

Estimating covariance in this situation is challenging, and the statistical
literature suggests several approaches \cite{bickel2008covariance,
ollerer2015robust, bien2011sparse, friedman2008sparse, bickel2008regularized,
hsieh2011sparse}. For speed and simplicity, we follow the guidance of
\cite{kolar2012consistent} for handling missing values and of
\cite{touloumis2015nonparametric} for regularization.

We begin by building a matrix of pair-wise empirical covariance. In this
matrix, the value of each element is computed as the covariance between a pair
of sensors. By filling the matrix, covariance is computed independently for all
sensor pairs. However, the resulting matrix does not necessarily describe
multi-dimensional covariance (i.e. it may not be positive definite), especially
with many missing values. To handle this, we shrink this matrix toward the
diagonal matrix of sensor variance. The magnitude of the shrinkage weight is
chosen to maximize the multivariate normal log-likelihood of the available
data. We subsequently use the shrunken matrix as $R$ in sensor fusion.

@@

\bibitem{bickel2008covariance}
Bickel PJ, Levina E.
\newblock Covariance regularization by thresholding.
\newblock The Annals of Statistics. 2008; p. 2577--2604.

\bibitem{ollerer2015robust}
{\"O}llerer V, Croux C.
\newblock Robust high-dimensional precision matrix estimation.
\newblock In: Modern Nonparametric, Robust and Multivariate Methods. Springer;
  2015. p. 325--350.

\bibitem{bien2011sparse}
Bien J, Tibshirani RJ.
\newblock Sparse estimation of a covariance matrix.
\newblock Biometrika. 2011;98(4):807--820.

\bibitem{friedman2008sparse}
Friedman J, Hastie T, Tibshirani R.
\newblock Sparse inverse covariance estimation with the graphical lasso.
\newblock Biostatistics. 2008;9(3):432--441.

\bibitem{bickel2008regularized}
Bickel PJ, Levina E.
\newblock Regularized estimation of large covariance matrices.
\newblock The Annals of Statistics. 2008; p. 199--227.

\bibitem{hsieh2011sparse}
Hsieh CJ, Dhillon IS, Ravikumar PK, Sustik MA.
\newblock Sparse inverse covariance matrix estimation using quadratic
  approximation.
\newblock In: Advances in Neural Information Processing Systems; 2011. p.
  2330--2338.

\bibitem{kolar2012consistent}
Kolar M, Xing EP.
\newblock Consistent covariance selection from data with missing values.
\newblock In: Proceedings of the 29th International Conference on Machine
  Learning (ICML-12); 2012. p. 551--558.

\bibitem{touloumis2015nonparametric}
Touloumis A.
\newblock Nonparametric Stein-type shrinkage covariance matrix estimators in
  high-dimensional settings.
\newblock Computational Statistics \& Data Analysis. 2015;83:251--261.

@@

% Don't include figures in the final version. This is just for preview.
\newgeometry{top=1.0in,left=1.0in,footskip=30pt}
\begin{figure}[p]
  \includegraphics[width=\textwidth]{../data/figures/sensor_heatmap_top.png}
  Figure 1 (top).
\end{figure}
\begin{figure}[p]
  \includegraphics[width=\textwidth]{../data/figures/sensor_heatmap_bottom.png}
  Figure 1 (bottom).
\end{figure}
\begin{figure}[p]
  \includegraphics[width=\textwidth]{../data/figures/all_nowcasts.png}
  Figure 2.
\end{figure}
\begin{figure}[p]
  \includegraphics[width=\textwidth]{../data/figures/accuracy_vs_sensors.png}
  Figure 3.
\end{figure}
\begin{figure}[p]
  \includegraphics[width=\textwidth]{../data/figures/accuracy_vs_ablation.png}
  Figure 4.
\end{figure}
\begin{figure}[p]
  \includegraphics[width=\textwidth]{../data/figures/accuracy_vs_abscission.png}
  Figure 5.
\end{figure}
